Out-of-Sample Comparisons of Overfit Models

### 2014-01-08 paper.tex
Fix typo in index of D_t
Move version info from Makefile to git hooks
This commit removes a script from the Makefile that generates
the commit date and version number and stores them in the file
VERSION.tex (which then is included in the main document). This
information is now generated by the git hooks:
- post-commit
- post-merge
- post-checkout

This approach is motivated by Brent Longborough's gitinfo package.
Redo indexing in Lemma A3
This commit rearranges the indexing in Lemma A3 so that alphabetical
order corresponds to temporal order. It also adds a missing index and
closes #29.

\input{VERSION.tex}
\title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, the 2011 \textsc{nber}/\textsc{nsf} Time-Series
    Conference, and in many seminars at \textsc{ucsd}, and espeically
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 \textsc{rfs} paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}

@@

\begin{lem}\label{lem-basic-coupling}
  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
  T, $s$, and $t$ with $t \geq s$, there exist random variables
  $D_s^*,\dots,D_t^*$ such that
  \begin{equation}\label{eq:coupling1}
    P[(D_s^*,\dots,D_t^*) \neq (D_s,\dots,D_t)] \leq \beta_{s-u}
  \end{equation}
  and
  \begin{equation}\label{eq:coupling2}
    \E(\phi(D_s^*,\dots, D_t^*) \mid \mathcal{F}_u ) =
    \int
    \phi(D_s,\dots,D_t) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
  \end{equation}
  almost surely for all measurable functions $\phi$ such that the
  expectations are finite, where
  \[ \mathbf{x} = (x_{s}', \dots, x_{t}')', \qquad
  \mathbf{y} = (y_{s+\h},\dots,y_{t+\h})',\] and $f$ is the
  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
 \begin{equation}\label{eq:coupling3}
   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
   \beta_{s-u}^{\rhoExp}, \qquad v = s,\dots,t.
 \end{equation}
\end{lem}

\begin{proof}
  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
  \ref{lem-extend-mp}.  Let $l = t-s$.  For any fixed values of $l$
  and $T$, the sequence of vectors
  \[ V_s = (y_{s+\h}, x_{s}', \dots, y_{s+l+\h}, x_{s+l}') \] is
  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
  that there is a random vector $V^*$ that is independent of
  $\mathcal{F}_u$, equal to $V_s$ in distribution, and satisfies
  \[\Pr[V^* \neq V_s] = \beta_{s-u}.\]

  Now define
  \begin{equation*}
    D_v^* =
    \begin{cases}
      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
    \end{cases}
  \end{equation*}
  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_s$.  Equations
  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
  construction, and (\ref{eq:coupling3}) follows from Lemma
  \ref{lem-extend-mp}.
\end{proof}

@@

And we can finish the proof with the following inequalities:
\begin{align*}
  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
  \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
  D_{t+l+R,R} - D_{t,t+l+R}^* \rVert_2 W(l/\gamma) \\&
  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
  = O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
\end{align*}
for some positive $u$.  The same argument holds for $Z_{2t}$.
As a result,
\[
E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma\Big) =
 o(b_T/\gamma) \to 0,
\]
as required.
\end{proof}

>>>>

% VERSION is generated by a post-commit hook and contains the git
% version info
\IfFileExists{VERSION}{
  \input{VERSION}
  \date{\dinfo\ (version \hinfo)}
  \markright{\dinfo\ (version \hinfo)}
}{}

\title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, the 2011 \textsc{nber}/\textsc{nsf} Time-Series
    Conference, and in many seminars at \textsc{ucsd}, and espeically
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 \textsc{rfs} paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}

@@

\begin{lem}\label{lem-basic-coupling}
  Suppose Assumptions \ref{asmp-1}--\ref{asmp-3} hold.  Then, for any
  T, $s$, $t$, and $u$ with $s < t \leq u$, there exist random
  variables $D_t^*,\dots,D_u^*$ such that
  \begin{equation}\label{eq:coupling1}
    P[(D_{t}^*,\dots,D_u^*) \neq (D_{t},\dots,D_u)] \leq \beta_{t-s}
  \end{equation}
  and
  \begin{equation}\label{eq:coupling2}
    \E(\phi(D_{t}^*,\dots, D_u^*) \mid \mathcal{F}_s ) =
    \int
    \phi(D_{t},\dots,D_u) f(\mathbf{x}, \mathbf{y})\ d\mathbf{x}\ d\mathbf{y}
  \end{equation}
  almost surely for all measurable functions $\phi$ such that the
  expectations are finite, where
  \[ \mathbf{x} = (x_{t}', \dots, x_{u}')', \qquad
  \mathbf{y} = (y_{t+\h},\dots,y_{u+\h})',\] and $f$ is the
  joint density of $(\mathbf{x}, \mathbf{y})$.  Moreover,
 \begin{equation}\label{eq:coupling3}
   \| D_v^* - D_v \|_2 \leq 2^{1+1/\rho} B_L
   \beta_{t-s}^{\rhoExp}, \qquad v = t,\dots,u.
 \end{equation}
\end{lem}

\begin{proof}
  The proof follows as a consequence of Lemmas \ref{lem-berbee} and
  \ref{lem-extend-mp}.  Let $l = u-t$.  For any fixed values of $l$
  and $T$, the sequence of vectors
  \[ V_{t} = (y_{t+\h}, x_{t}', \dots, y_{t+l+\h}, x_{t+l}') \] is
  absolutely regular of size $\rho/(\rho-2)$.  Berbee's Lemma implies
  that there is a random vector $V^*$ that is independent of
  $\mathcal{F}_s$, equal to $V_{t}$ in distribution, and satisfies
  \[\Pr[V^* \neq V_{t}] = \beta_{t-s}.\]

  Now define
  \begin{equation*}
    D_v^* =
    \begin{cases}
      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1R}) - L(y_{v+\h}^* -
      x_{2v}^{*\prime} \hat{\theta}_{2R}) & v \leq T \\
      L(y_{v+\h}^* - x_{1v}^{*\prime} \hat{\theta}_{1T}) - L(y_{v+\h}^* -
      x_{2v}^{*\prime} \hat{\theta}_{2T}) & v > T
    \end{cases}
  \end{equation*}
  with $y_{v+\h}^*$ and $x_{iv}^*$ denoting the elements of $V^*$
  corresponding to $y_{v+\h}$ and $x_{iv}$ in $V_{t}$.  Equations
  (\ref{eq:coupling1}) and (\ref{eq:coupling2}) are satisfied by
  construction, and (\ref{eq:coupling3}) follows from Lemma
  \ref{lem-extend-mp}.
\end{proof}

@@

And we can finish the proof with the following inequalities:
\begin{align*}
  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
  \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
  D_{t+l+R} - D_{t,t+l+R}^* \rVert_2 W(l/\gamma) \\&
  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
  = O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
\end{align*}
for some positive $u$.  The same argument holds for $Z_{2t}$.
As a result,
\[
E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma\Big) =
 o(b_T/\gamma) \to 0,
\]
as required.
\end{proof}
